\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-15 papers/sbst23/paper_sbst23.tex
fix(results): mention average coverage instead of median coverage

The coverage \EVOSUITE achieved on the \cuts classes distributed across the \projects
projects used in the competition is illustrated in Figure~\ref{fig:results30} for a search
budget of \budgetShort, and in Figure~\ref{fig:results120} for a budget of \budgetLong.
The median line and branch coverage for the \budgetShort budget is
\medLinesCoverageRatioShort and \medConditionsCoverageRatioShort, and
increases to \medLinesCoverageRatioLong and \medConditionsCoverageRatioLong
for the \budgetLong budget. The median mutation coverage is \SI{0}{\percent} in
both cases, and equal to all the other tools used in the competition.

>>>>

The coverage \EVOSUITE achieved on the \cuts classes distributed across the \projects
projects used in the competition is illustrated in Figure~\ref{fig:results30} for a search
budget of \budgetShort, and in Figure~\ref{fig:results120} for a budget of \budgetLong.
The average line and branch coverage for the \budgetShort budget is
\avgLinesCoverageRatioShort and \avgConditionsCoverageRatioShort, and
increases to \avgLinesCoverageRatioLong and \avgConditionsCoverageRatioLong
for the \budgetLong budget. The average mutation coverage is \avgMutantsCoverageRatioShort
and \avgMutantsCoverageRatioLong, respectively.
